An Interactive Tutorial on Hash Array Mapped Tries

### 2024-08-23 paper/paper.tex
paper

We reimplemented~\footnote{\url{https://github.com/frenchy64/optimized-kw-maps}}
the \texttt{PersistentHashMap} class from
the Clojure standard library in Clojure---it was originally
written in Java.
This is not the first reimplementation. ClojureScript
features similar pure-Clojure port in its standard library,
and several other languages have ported their own versions
based on Clojure's original implementation.

>>>>

We ported~\footnote{\url{https://github.com/frenchy64/hamt-tutorial}}
the \texttt{PersistentHashMap} Java class from
the Clojure standard library to pure Clojure.
This is not the first reimplementation. ClojureScript
features similar pure-Clojure port in its standard library,
and several other languages have ported their own versions
based on Clojure's original implementation.
